---
title: "Homework 4"
author: "Anushka Canfield"
date: "2024-02-08"
output: html_document
---


### **Question One**: 
```
Assign each expression to the value of the variable z and print the value stored in z.
```

```{r}
x <- 1.1
a <- 2.2
b <- 3.3
``` 

1.a 
$z=x^{a^b}$ 
```{r}
z=x^{a^b}
z
```

1.b 
$z=(x^a)^b$  
```{r}
z =(x*(a*b))
z
```


1.c 
$3x^3 + 2x^2 + 1$ 
```{r}
z =3*(x*x*x) + 2*(x*x) + 1
z
```

### **Question Two**: 
```
Use the rep and seq functions to create the vectors outlined:
```
2.a    (1, 2, 3, 4, 5, 6, 7, 8, 7, 6, 5, 4, 3, 2, 1)

```{r}
a <- c(seq(1:8), seq(7:1))
a
```


2.b    (1, 2, 2, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 5)

```{r}
b <- rep(seq(1,5),times=seq(1,5))
b
```


2.c    (5, 4, 4, 3, 3, 3, 2, 2, 2, 2, 1, 1, 1, 1, 1)

```{r}
c <- rep(seq(5,1),times=seq(1,5))
c

```

### **Question Three: **

```
Create a vector of two random uniform numbers. In a spatial map, these can be interpreted as x and y coordinates that give the location of an individual (such as a marked forest tree in a plot that has been mapped). Using one of R’s inverse trigonometry functions (asin(), acos(), or atan()), convert these numbers into polar coordinates 
```

```{r}
cartesian <- runif(2)    #X and Y

x = cartesian[1]
y = cartesian[2]

r = sqrt((x^2 + y^2))
theta = atan(y/x)

paste("The polor coordinates are:", r, theta)
```

### **Question Four:**

```
The queue represents the animals and their order on Noah's Ark. Update the lineup as more animals appear. 
```
The queue:
```{r}
queue <- c("sheep", "fox", "owl", "ant")

```

4.a the serpent arrives and gets in line
```{r}
queue <- c(queue, "serpent")
queue 
```

4.b the sheep enters the ark
```{r}
queue <- c(queue[-1])
queue

```

4.c the donkey arrives and talks his way to the front of the line
```{r}
queue <- c("donkey",queue)
queue
```

4.d the serpent gets impatient and leaves
```{r}
queue <- (queue[-(length(queue))])
queue
```

4.e the owl gets bored and leaves
```{r}
queue <- c(queue[1], queue[2], queue[4])
queue

```

4.f the aphid arrives and the ant invites him to cut in line.
```{r}
queue <- c(queue[1:2], "aphid", queue[3])
queue
```

4.g Finally, determine the position of the aphid in the line.
```{r}
queue <- length(queue[-1])
queue
```

### Question Five:

```
Use R to create a vector of all of the integers from 1 to 100 that are not divisible by 2, 3, or 7
```

```{r}

n <- seq(1,100)

vector <- which(n%% 2 & n %% 3 & n %% 7)
vector
```


